Usage metrics

### 2021-04-13 analysis/normalized.Rmd
Update normalized expressions with last run results
Fix Kaggle usage metrics (top function)

@@

Minimized:
```{r}
widespread_minimized <- E_cano %>%
  group_by(minimized) %>%
  summarize(n_call_sites = n_distinct(src_ref), 
            proportion = ratio(n_call_sites, nb_call_sites), 
            n_packages = n_distinct(ev_package),
            n_operations = round(mean(n_op, na.rm=TRUE)), 
            med_operations = median(n_op, na.rm = TRUE),
            percent_envir = ratio(n_distinct(cur_data()$src_ref[!is.na(cur_data()$envir)]),  n_call_sites), 
            percent_envir_calls = ratio(sum(!is.na(envir)), n()), 
            env_diversity = n_distinct(envir), 
            percent_envir_parent_frames = ratio(n_distinct(cur_data()$src_ref[str_starts(cur_data()$environment_class, fixed("caller-"))]),  n_call_sites),
            percent_envir_non_parentframe = ratio(n_distinct(cur_data()$src_ref[!is.na(cur_data()$envir) & cur_data()$envir != "parent.frame()"]),  n_call_sites)) %>% 
  arrange(desc(n_call_sites))

>>>>

  # We currently merge minimized expressions F(F(X)) and F(F())
  N <- N %>% mutate(minimized = if_else(minimized == "F(F())", "F(F(X))", minimized))

@@

Minimized:
```{r}
widespread_minimized <- E_cano %>% filter(type != "bytecode") %>% #Only two sites anyway
  group_by(minimized) %>%
  summarize(n_call_sites = n_distinct(src_ref), 
            proportion = ratio(n_call_sites, nb_call_sites), 
            n_packages = n_distinct(ev_package),
            n_operations = round(mean(n_op, na.rm=TRUE)), 
            med_operations = median(n_op, na.rm = TRUE),
            percent_envir = ratio(n_distinct(cur_data()$src_ref[!is.na(cur_data()$envir)]),  n_call_sites), 
            percent_envir_calls = ratio(sum(!is.na(envir)), n()), 
            env_diversity = n_distinct(envir), 
            percent_envir_parent_frames = ratio(n_distinct(cur_data()$src_ref[str_starts(cur_data()$environment_class, fixed("caller-"))]),  n_call_sites),
            percent_envir_non_parentframe = ratio(n_distinct(cur_data()$src_ref[!is.na(cur_data()$envir) & cur_data()$envir != "parent.frame()"]),  n_call_sites)) %>% 
  arrange(desc(n_call_sites))

### 2021-04-13 analysis/usage.Rmd
Fix Kaggle usage metrics (top function)

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/package/
  calls_path: summarized.fst
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

top_func <- frequent_funcs %>% .[1,]

>>>>

---
title: "Usage metrics"
author: "Pierre Donat-Bouillud"
output:
    html_document:
        gallery: false
        toc: true
        toc_depth: 3
        toc_float: true
        df_print: paged
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
params:
  base_dir: Data/kaggle/
  calls_path: summarized.fst
  corpus_path: corpus.txt
  static_path: evals-static.csv
  force_rebuild: TRUE
---

@@

top_func <- frequent_funcs %>% filter(!is.na(func)) %>% .[1,]
